\documentclass[defaultstyle,11pt]{thesis}

\usepackage{amsmath}
\usepackage{amssymb}		% to get all AMS symbols
\usepackage{graphicx}		% to insert figures
\usepackage{hyperref}		% PDF hyperreferences??
\newcommand{\ubar}[1]{\text{\b{$#1$}}}
\usepackage{bbm}
\usepackage{multicol}
\usepackage[dvipsnames]{xcolor}
\usepackage{diagbox}

%%%%%%%%%%%%   All the preamble material:   %%%%%%%%%%%%

\title{Deep Generative Modeling for Probabilistic Electricity Price Forecasting}

\author{Nicholas}{Elsasser}

\otherdegrees{B.S., University of Colorado Boulder, 2022}

\degree{Masters of Science}		%  #1 {long descr.}
	{M.S., Computer Science}		%  #2 {short descr.}

\dept{Department of}			%  #1 {designation}
	{Computer Science}		%  #2 {name}

\advisor{Prof.}				%  #1 {title}
	{Claire Monteleoni}			%  #2 {name}

\reader{Sriram Sankaranarayanan}		%  2nd person to sign thesis
\readerThree{Kyri Baker}		%  3rd person to sign thesis

\abstract{  \OnePageChapter	% because it is very short
    Electricity price forecasting in deregulated nodal electricity markets is a significant problem for market operators
    and market participants.
    Uncertainty in key market factors can propagate to significant price events that prove
    difficult to predict and hedge against.
    In this work, we propose and investigate a joint conditional probabilistic methodology for day-ahead price
    forecasting across a set of geographically distributed price nodes using recent advancements in deep generative
    modeling.
    We motivate and assess strategies that can be used to improve and adjust probabilistic forecast
    results and compare our proposed methodology against open access state-of-the-art statistical and
    machine learning  benchmarks in energy price forecasting literature as well as a physics-based, commercially
    available optimimal economic dispatch forecasting tool.
}

\dedication[Dedication]{	% NEVER use \OnePageChapter here.
	To all of the fluffy kitties.
	}

\acknowledgements{	\OnePageChapter	% *MUST* BE ONLY ONE PAGE!
	Here's where you acknowledge folks who helped.
	But keep it short, i.e., no more than one page,
	as required by the Grad School Specifications.
	}

% \IRBprotocol{E927F29.001X}	% optional!

\ToCisShort	% use this only for 1-page Table of Contents

\LoFisShort	% use this only for 1-page Table of Figures
% \emptyLoF	% use this if there is no List of Figures

\LoTisShort	% use this only for 1-page Table of Tables
% \emptyLoT	% use this if there is no List of Tables

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%       BEGIN DOCUMENT...         %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\input macros.tex

\input introduction.tex
\input background.tex
\input methodology.tex
\input experiments.tex
\input conclusion.tex

%%%%%%%%%   then the Bibliography, if any   %%%%%%%%%
\bibliographystyle{plain}	% or "siam", or "alpha", etc.
\nocite{*}		% list all refs in database, cited or not
\bibliography{refs}		% Bib database in "refs.bib"

%%%%%%%%%   then the Appendices, if any   %%%%%%%%%
\appendix

\input appendix_pricenodes.tex
\input appendix_loadzones.tex
\input appendix_weatherstations.tex

\input appendix_hyperparams.tex

\end{document}
